Viscous Transport in Eroding Porous Media

### 2019-04-25 docs/transport/erosion_transport.tex
type the numerical method of exterior part
working on transport paper

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation}
\label{s:formulation}
Similar to the JCP methods paper.  However, need to put everything into
complex variables formulation so that we can use Barycentric ideas.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral equation formulation} 
\label{sec:bies}
Add an introduction why we do not use the double-layer potentials of Stokes equations but the double-layer potentials of Laplace equations to solve Stokes equation when we use Barycentric approach (or complex variable approach).
\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }

Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.

Consider a Laplace's equations with Dirichlet boundary condition
\begin{equation}\label{Laplace}
  \begin{cases}
    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
  \end{cases}
\end{equation}

Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
The double-layer potential which solves \eqref{Laplace} is 
\begin{align*}
\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})ds_y,
%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})ds_y,\\ \\
%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})ds_y\\ \\
%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})ds_y 
\numberthis\label{DLP:real}
\end{align*}
where $\sigma$ is the density function on the boundary $\Gamma$.

Consider a Cauchy integral 
\begin{equation}\label{CI}
v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
\end{equation}
where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}ds_y$. It can be showed that 
the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}.

\subsubsection{From Stokes DLP to Laplace DLPs}

Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.

The Stokes double-layer potential  is
\begin{equation}\label{StokesDLP1}
\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d s_y.
\end{equation}
We could rewrite the Stokes DLP in terms of the Laplace DLP as
\begin{align*}\label{StokesDLP2}
\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y. \numberthis
\end{align*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Governing Equations}
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
velocity} \\
\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
&&\mbox{\em erosion model}.
\end{split}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing on our previous work~\cite{qua-moo2018}, we use a completed
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) ds_\yy,
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
density function.  The double-layer potential itself can not represent
all solutions of the incompressible Stokes equations.  Therefore, we
complete the integral equation formulation following the work of Power
and Miranda~\cite{pow-mir1987}.  The completion depends on the
Stokeslets and rotlets
\begin{align}
  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \qquad
  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
\end{align}
where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
\|\rr\|$.  Then, the solution of the Stokes equation is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx),
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
    \NN_0(\eeta](\xx), \qquad \xx \in \bd\Omega, \\
  \lambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy) ds_\yy \qquad \ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp  \eeta(\yy) ds_\yy 
    \qquad \ell = 1,\ldots,M.
\end{align}
The Stokes double-layer potential can be written as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta)ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy,
\end{align}
and this formulation is convenient since each of the integrals can be
written as a Laplacian double-layer potential,
\begin{align}
  \DD[\tau](\xx) = -\frac{1}{2\pi} \int_{\Gamma} \pderiv{}{\nn_\yy}
    \log(\rho) \tau(\yy) ds_\yy.
\end{align}
Finally, by identifying $\RR^2$ with $\CC$, for purely real $\tau$, the
Laplacian double-layer potential can be written as the real part of a
Cauchy integral
\begin{align}
  \DD[\tau](x) = \Re (v(x)),
  \qquad \text{where} \qquad
  v(x) = \frac{1}{2\pi i} \int_\Gamma \frac{\tau(y)}{x - y} dy.
\end{align}
Therefore, the Stokes double-layer potential can be written as five
Cauchy integrals and their derivatives with the density functions $\yy
\cdot \nn$, $\eta_1$, and $\eta_2.$

Since the rate of erosion is proportional to the shear stress, we also
require the gradient of the Stokes double-layer potential $\nabla
\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the shear
stress of the double-layer potential velocity is
\begin{align}
  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
\end{align}

\section{New Section}
A standard discretization of these equations approximates the
double-layer potential with the trapezoid rule.  This quadrature rule is
appropriate if the integrands are sufficiently smooth, where the
smoothness depends on the number of discretization points.  However,
given a fixed resolution, if the target point $\xx$ is too close to $\bd
\Omega$, the trapezoid rule becomes inaccurate and the overall method
becomes unstable.  There have been a variety of near-singular
integration schemes developed, and we extend a method first outlined by
Barnett et al.~\cite{bar-wu-vee2015} which we will call the {\em
Barycentric quadrature rule}.  Here, we briefly describe this quadrature
method, and then derive a necessary extension to simulate erosion.

The Barycentric quadrature rule was first described for the single- and
double-layer potentials corresponding to Laplace's equation.

A quadrature scheme for $v(x)$, for a target point $x$, is
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^N 
    w_j \frac{\tau(y_j)}{x - y_j},
\end{align}
where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
quadrature nodes.  If the trapezoid rule is used, the quadrature rule
has spectral accuracy.  However, for a fixed resolution $N$, the error
grows without bound as $x$ approaches $\Gamma$.  As outline by Barnett
et al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
Barycentric quadrature rule
\begin{align}
  v(x) \approx \frac{\sum_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
  v'(x) \approx \frac{\sum_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum_{j=1}^N \frac{1}{y_j-x}w_j}, 
\end{align}
is used, where $x$ is a target point that is interior to $\Gamma$,
and $v_j^-$ is the value of $v(y_j)$.  Modifications of this formula
exist if $x$ is exterior to $\Gamma$.

Similar to the JCP methods paper.  However, need to put everything into
complex variables formulation so that we can use Barycentric ideas.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral equation formulation} 
\label{sec:bies}
Add an introduction why we do not use the double-layer potentials of Stokes equations but the double-layer potentials of Laplace equations to solve Stokes equation when we use Barycentric approach (or complex variable approach).

%\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }
%
%Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.
%
%Consider a Laplace's equations with Dirichlet boundary condition
%\begin{equation}\label{Laplace}
%  \begin{cases}
%    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
%    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
%  \end{cases}
%\end{equation}
%
%Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
%The double-layer potential which solves \eqref{Laplace} is 
%\begin{align*}
%\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})ds_y,
%%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})ds_y,\\ \\
%%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})ds_y\\ \\
%%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})ds_y 
%\numberthis\label{DLP:real}
%\end{align*}
%where $\sigma$ is the density function on the boundary $\Gamma$.
%
%
%Consider a Cauchy integral 
%\begin{equation}\label{CI}
%v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
%\end{equation}
%where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}ds_y$. It can be shown that 
%the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}. 
%
%
%\subsubsection{From Stokes DLP to Laplace DLPs}
%
%Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
%
%
%The Stokes double-layer potential  is
%\begin{equation}\label{StokesDLP1}
%\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d s_y.
%\end{equation}
%We could rewrite the Stokes DLP in terms of the Laplace DLP as
%\begin{align*}\label{StokesDLP2}
%\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
%&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y. \numberthis
%\end{align*}
%
